---
title: "first_R_presentation"
output: 
  beamer_presentation: 
    colortheme: orchid
    fonttheme: structurebold
    theme: Antibes
---



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- \color{orange} Bullet 1
- \color{green} Bullet 2
- \color{red} Bullet 3

## Slide with R Output

```{r cars, echo = FALSE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Incramental Billets
> - almost
> - like
> - animation

##Using bigskip

For ...

\bigskip   
\bigskip   
\bigskip   
\bigskip   

Emphasis

## Trial Figure In \LaTeX

 \begin{picture}(320,250)
 \put(50,100){\includegraphics[height=8cm]{CO_lake.jpg}}
 \put(00,50){\begin{minipage}[t]{1\linewidth}
 \end{minipage}}
 \end{picture}
 
## Trial Figure In \LaTeX (2)

 \begin{picture}(320,250)
 \put(85,75){\includegraphics[height=6cm]{CO_lake.jpg}}
 \put(00,60){\begin{minipage}[t]{1\linewidth}
 {Choose a point on the unit circle. Connect it to the origin with a line of length one, and denote the angle between that line and the horizontal coordinate axis by $\theta$.}
 \end{minipage}}
 \end{picture}
 
## Trial Figure In \LaTeX (3)

 \begin{picture}(320,250)
 \put(0,20){\includegraphics[height=8cm]{CO_lake.jpg}}
 \put(180,180){\begin{minipage}[t]{0.4\linewidth}
 {Choose a point on the unit circle. Connect it to the origin with a line of length one, and denote the angle between that line and the horizontal coordinate axis by $\theta$.\textit{Levi} -testbf{double the trouble}}
 \end{minipage}}
 \end{picture}
 




