---
title: 'Homework #4'
author: "cuden"
date: "9/12/2018"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##1.

```{r,  echo=TRUE}
x <- 1.1
a <- 2.2
b <- 3.3
#a
z <- x^(a^b)
print(z)
#b
z <- (x^a)^b
print(z)
#c
z <- 3*x^3+2*x^2+1
print(z)
```

##2

```{r, echo=TRUE}
#a
z <- seq(from=1, to=8, by=1)
z <- rep(x=c(z[1:8],z[7:1]))
print(z)
#OR
z <- seq(from=1, to=8, by=1)
y <- c(z[7:1])
z <- c(z,y)
print(z)

#b
z <- seq(from=1, to=5, by=1)
z <- rep(x=z, times=z)
print(z)

#c
z <- seq(from=1, to=5, by=1)
z <- rep(x=c(z[5:1]), times=c(z[1:5]))
print(z)

```

##3

```{r, echo=TRUE}
# Polar coordinates can be written as ordered pair, (r,theta). r is distance form pole to point P. Theta is the angle measured from polar axis to line that passes through pole. 

polarCoord <- runif(2) #make a matrix of two random uniform numbers
print(polarCoord)
x <- polarCoord[1] #first number in martix is x
y <- polarCoord[2] #second number in matrix is y

r <- sqrt(x^2+y^2)
theta <- atan(x/y)

print(r)
print(theta)

```


##4

```{r,echo=TRUE}
queue <- c("sheep", "fox", "owl", "ant")
print(queue)

#a Serpant arrives 
queue <- c(queue,"serpant")
print(queue)

#b Sheep enters the ark
queue <- c(queue[2:5])
print(queue)

#c Donkey talks his way to the front
#queue[1] <- "donkey" this replaces the first column with donkey
queue <- c("donkey",queue) 
print(queue)

#d The serpant leaves
queue <- queue[-5]
print(queue)

#e The owl gets bored and leaves
queue <- queue[-3]
print(queue)

#f Ant lets aphid cut the line
queue <- c(queue[1:2],"aphid",queue[3])
print(queue)

#g In what postition is the aphid?

#match(c("aphid",queue))

#regexpr("aphid",queue)

#ind("aphid",queue)
```


##5

```{r,echo=TRUE}
# Use r to create a vector of all integers from 1 to 100 not divisible by 2,3 or 7.

z <- c(1:100)
z

# which(!z%/%2==0) gives you and index of elements in Z not (!) divisible (%%) by 2. 
# z[which(!z%/%2==0)] gives you the values in the index. so,
a <- z[which(!z%/%2==0)]
b <- z[which(!z%/%3==0)]
c <- z[which(!z%/%7==0)]

# Use the & operator to combine all logical operations:

d <- z[which(!z%%2==0 & !z%%3==0 & !z%%7==0)]

print(d)
```

##6
Find:(\s{2,})

Replace: ,

##7

Find: (\w+)(\W)(\s)(\w+)(\W)(\s)(..*)(\s|\N)

Broke each line into 6 elements:
1. a word more than one character long
2. not a character (the comma)
3. space
4. word
5. not character (comma)
6. space
7. rest of the line
8. space OR (|) line break

Replace: \1\3\4\6(\7)\8
 

##8

Find: (\W)(\w{2})(\d{1})(\s)

Replace:\1\2\3\n

Find:((\d{4})(\s{1})((\w+\s\w+)|(\w+\s\w+\s\w+\s\w+))(\W)(\w{2})(\d{1})

Replace: \3_\1\5\6\7\8  SO CLOSEEE!!!

##9

Find: (.)(\w+,)(\w+,)(\d+.\d,)

(.) indicates "any charactes" -in this case, the first letter of the first word. 

Replace: \1_\2

Find: (.)(\w+,)(\w{4})(\w+)(,)(\d+.\d,)

I broke the second word into two: the first four letters (\w{4}) and then the rest of the word (\w+)

Replace: \1_\3\5